---
title: "Documentation"
author: "Group 11"
output: html_document:
          toc: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Importing the data

## Data preparation

## Creation of the final data set





### calculating positions and distances

(TODO: positions)

Since the positions of the different sites are given in longitude and latitude in degrees, the distance between two points can not be calculated with the cartesian distance in cartesian coordinates. For this reason the there is a function which calculates the distance between two points using a haversine curve and casts it to a integer in kilometres.

```{r}

# calculate shortest distances between points A and B given by longitude and latitude in degrees to km via Haversine
calc_distance_in_km <- function(lonA, latA, lonB, latB) {
  as.integer(distHaversine(cbind(lonA,latA),cbind(lonB,latB)))/1000
}
# example:
calc_distance_in_km(52, 13, 50, 7)
```

This function is then used on the plants for single parts, components, OEM, State capital and Distribution center, and gets also added to the final data set.

```{r}
# calculate distances of material flow

fz_komp_teile_geo_dist <- fz_komp_teile_geo %>%
  mutate(Distanz_Einzelteil_zu_Komponente_in_km = calc_distance_in_km(Längengrad_Einzelteil, Breitengrad_Einzelteil, Längengrad_Komponente, Breitengrad_Komponente)) %>%
  mutate(Distanz_Komponente_zu_Fahrzeug_in_km = calc_distance_in_km(Längengrad_Komponente, Breitengrad_Komponente, Längengrad_Fahrzeug, Breitengrad_Fahrzeug)) %>%
  mutate(Distanz_Fahrzeug_zu_Hauptstadt_in_km = calc_distance_in_km(Längengrad_Fahrzeug, Breitengrad_Fahrzeug, Längengrad_Hauptstadt, Breitengrad_Hauptstadt))%>%
  mutate(Distanz_Hauptstadt_zu_Gemeinde_in_km = calc_distance_in_km(Längengrad_Hauptstadt, Breitengrad_Hauptstadt, Längengrad_Gemeinde, Breitengrad_Gemeinde ))

```


The final data set can now be viewed and saved as a .csv-file for later use in the shiny app:

```{r}
summary(fz_komp_teile_geo)
fwrite(fz_komp_teile_geo_dist,file=paste0(getwd(),"/Final_Data_Group_11.csv"), row.names = FALSE)
```



## Evaluation



The finished data set can now be saved as well as loaded.

```{r}
source("Case_Study_App_load_data.R")
```


### Visualisation of material flow

For evaluation of the data it is helpful to visualize data in different ways. In the case study were different types of plots developed for the given data. They show information about the distribution chain and material flow of the different levels of car manufacturing.

#### Map

To visualize the complex distribution chain of car manufacturing a map with a connection graph can be helpful. The map shows Germany and can plot all involved points in germany for a given vehicle ID. Furthermore the app can overlay the distribution chain of the shortest, longest or median total distance for comparison. The connections of the different levels can be turned on or off as well, if e.g. only the connection from single part plants to component plants shall be compared. Since there are different types of vehicles in the data the comparison of shortest, longest or median total distances can be enabled to only show the according paths of the same vehicle type as entered.


#### Boxplot

The boxplot shall show the material flow over the different phases of production. Before a single part gets assembled to a component it has to travel to the according component plant. In the same way, components have to travel to the OEM site, as well as the finished vehicles need to go to the state capital from which they go to the final distribution center. 

For this, the data is grouped by single parts, components and vehicle IDs and 

```{r , echo=FALSE}
boxplot_from_selected(captions_list, dist_vs_type, levels_selected=1:4) 
```

The plot shows how similar the distances between single parts and components are both in median as well as deviation. Even the median of the distances between the OEM and State capital which is about 260 km as well as its deviation is very similar. All in all however is the distance a vehicle travels to the final distribution center in median about 90 km longer. And while most cars need to travel around this median within an interval of 200km (first to third quantile), the maximum travel distance is much greater.


#### Material flow of components



## Result




